Gafo-cc data processing

### 2023-12-13 analysis/gafo-cc-data-processing.Rmd
update figures

```
# Merge
```{r}
merge_raw_data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  data_nz, 
  data_tur,
  data_cong
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))

>>>>

```
# Uganda

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/uganda/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)

# convert json files to tibbles
raw_data_uganda <- tibble()
for (f in files) {
  jf <- paste("../../raw_data/gafo-cc/uganda/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  raw_data_uganda <- bind_rows(raw_data_uganda, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_uganda <- raw_data_uganda %>%

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) %>%
  mutate(subjID = ifelse(subjID == "ugaand04", "ugand004", subjID),
         subjID =as.factor(subjID))%>%
  select(-touchScreen)%>%
  mutate_if(is.character, as.factor)%>% 
  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

unique(tidy_data_uganda$subjID)
```

```{r}
tidy_data_uganda%>%
  filter(trialType == "test")%>%
  group_by(subjID)%>%
  summarise(n = n())

tidy_data_uganda%>%
  filter(trialType == "test")%>%
  summarise(n = n_distinct(subjID))

```{r demographics}
raw_demographics_uganda <- read_xlsx("../../raw_data/gafo-cc/uganda/gafo_uganda_participants.xlsx", sheet = 1)[-1, ]

tidy_demographics_uganda <- raw_demographics_uganda %>%
  rename(subjid = id)%>%
  mutate_all(tolower)%>%
  filter(status == "keep")%>%
  mutate(
    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    screen = as.numeric(screen), 
    touchscreen = as.numeric(touchscreen),
    household = as.numeric(household), 
    children = as.numeric(children),
    younger_children = as.numeric(younger_children)
  )  %>%
  select(-c(test_date, birth_date, comment, age))%>%
  filter(!is.na(ageinyears))

```{r}
data_uganda <- tidy_demographics_uganda%>%
  left_join(tidy_data_uganda%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_uganda%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

# Merge
```{r}
merge_raw_data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  data_nz, 
  data_tur,
  data_cong,
  data_uganda
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))
